### 2019-08-12 Thesis/pages/experiments.tex
Changes; - Added more content to the experiment section of the paper - Updated and added new misc scripts

\section{Scallion vs GreenOnion}
% Show that the bloom filter blows Scallion out of the water
\textbf{TODO}

\section{Distribution of vulnerable keys}
\textbf{TODO}

\section{Average number of permutations for each metric}
\textbf{TODO}

\section{Metric Performance - Results}
As discussed in Section \ref{exp:metric} the goal of the experiment was the cull the number of metrics to be assessed in the following experiment. This section will discuss the demographics of participants alongside the subsequent results.

@@

\section{Experiment 2}
\label{sec:exp2}
% Demographic
% Results

@@

\section{Generation of keys}
To demonstrate that the the generation of the near collision keys is not only theoretical actual generation of keys was performed using GreenOnion. A random metric was selected from the three carried forward from the first experiment. Alongside this a random uncontrolled key was generated as the simulated attack target (See Appendix \ref{appendix:uncontrolled_key} for the armor public key). Then for each attack level (0 static, 1 static, 2 static) a key was computed. NYSIIS was chosen as the selected metric. To expedite the process an initial search was performed for controlled keys that had the highest number of permutations, this was due to the demonstration of the actual generation of keys. Producing near-matching keys that have a very small number of potential matches, therefore, adds very little to this demonstration with a large computation cost.

>>>>

\section{Scallion vs GreenOnion}
This section will compare Scallion and the newly designed GreenOnion ability to search for a large number of potential keys.

Table \ref{tab:scallion_speed} shows the speed decline as the number of keys increase. Any number of keys over 45 resulted in a crash to the program.

\todo{Add screenshot of the exception}

\begin{table}[!h]
    \centering
    \begin{tabular}{|ll|}
        \hline
        \textbf{Scallion} & \\
        \hline
        OS & Windows 10 (May 2019) \\
        Version & Scallion-2.0\footnote{\url{https://github.com/lachesis/scallion/raw/binaries/scallion-v2.0.zip}} \\
        \hline
        \textbf{GreenOnion} & \\
        \hline
        OS & Linux Mint (Version: TODO) \\ 
        \hline
        \textbf{Hardware} & \\
        \hline
        GPU & GTX 750 Ti  \\
        CPU & AMD FX-6300 \\
        \hline
    \end{tabular}
    \caption{Testing environment}
\end{table}

\begin{table}[!h]
    \centering
    \begin{tabular}{|ll|}
        \hline
        \textbf{Number of keys} & \textbf{Speed} \\
        \hline
        1 & 1001.3 MH/s \\
        5 & 784.3 MH/s \\
        10 & 707.9 MH/s \\
        15 & 628.2 MH/s \\
        20 & 526.5 MH/s \\
        25 & 503.8 MH/s \\
        30 & 473.1 MH/s \\
        35 & 432.6 MH/s \\
        40 & 404.9 MH/s \\
        45+ & \textit{N/A} \\
        \hline
    \end{tabular}
    \caption{Scallion's speed decline}
    \label{tab:scallion_speed}
\end{table}
\todo{Plot scallion speed decline}

\todo{Show the maximum number of keys the tool can achive}

\section{Experiment 1 - Metric performance}
As discussed in Section \ref{exp:metric} the goal of the experiment was the cull the number of metrics to be assessed in the following experiment. This section will discuss the demographics of participants alongside the subsequent results.

@@

\section{Experiment 2 - Simulated attacks}
\label{sec:exp2}
% Demographic
% Results

@@

\section{Average number of near-collision keys for each metric}
In order to predict the effectiveness of the attack over a wide variety of keys the number of average near-matches requires computation. Table \ref{tab:average_perm} shows the average keys for each metric. The ``Compute Time'' is the computation time required for a single mid range (2000MH/s) GPU.

\begin{table}[!h]
    \centering
    \begin{tabular}{|lllll|}
        \hline
        \textbf{Metric} & \textbf{Attack Type} & \textbf{Mean permuations} & \textbf{$\sigma$} & \textbf{Compute Time} \\
        \hline
        NYSIIS &&&& \\
        \hline
        & 0 static & 1963.07 & 24769.48 & ~~27.19 days \\
        & 1 static & 448.37 & 4316.57 & 119.14 days \\
        & 2 static & 98.07 & 550.44 & ~~~~1.49 years \\
        \hline

        Metaphone &&&& \\
        \hline
        & 0 static & 27138.78 & 529229.35 & ~~~~1.97 days \\
        & 1 static & 2822.74 & 23932.39 & ~~18.91 days \\
        & 2 static & 339.84 & 1730.97 & ~~15.45 days \\
        \hline

        Levenshtein &&&& \\
        \hline
        & 0 static & 293.92 & 2158.24 & 182.17 days \\
        & 1 static & 102.75 & 719.28 & ~~~~1.43 years \\
        & 2 static & 35.53 & 120.71 & ~~~~4.18 years \\
        \hline

    \end{tabular}
    \caption{Each metric's average near-collision keys}
    \label{tab:average_perm}
\end{table}

As it can be seen metrics like Levenshtein have a low overall average and would require much more attacker resources to become feasible. However, metaphone has attacks that could be computed on average in under 2 days

\section{Distribution of vulnerable keys}
As discussed in the design of the second experiment (See Section \ref{sec:exp2}) the attacks sampled from a list of `vulnerable keys'. These vulnerable keys were created using real keys extracted from PGP key servers. These keys were then randomly sampled and used to create the combined key as discussed in Section \ref{sec:pep}. 100,000 random key pair were as the total sample, and any vulnerable keys for each attack level were recorded.

\todo{Reference David's work}

\begin{table}[!h]
    \centering
    \begin{tabular}{|lll|}
        \hline
        \textbf{Attack Type} & \textbf{Metric} & \textbf{Vulnerable \%} \\
        \hline 
        2 static (152) && \\ 
        & Levenshtein & ~~4.295\% \\
        & Metaphone & 24.095\% \\
        & NYSIIS & 10.441\% \\
        \hline
        1 static (1525) && \\ 
        & Levenshtein & ~~0.827\% \\
        & Metaphone & 15.569\% \\
        & NYSIIS & ~~4.341\% \\
        \hline
        0 static (15250) && \\ 
        & Levenshtein & ~~0.157\% \\
        & Metaphone & 10.202\% \\
        & NYSIIS & ~~1.824\% \\
        \hline
    \end{tabular}
    \caption{Number of vulnerable keys per metric}
\end{table}

\section{Generation of keys}
To demonstrate that the the generation of the near collision keys is not only theoretical actual generation of keys was performed using GreenOnion. A random metric was selected from the three carried forward from the first experiment. Alongside this a random uncontrolled key was generated as the simulated attack target (See Appendix \ref{appendix:uncontrolled_key} for the armor public key). Then for each attack level (0 static, 1 static, 2 static) a key was computed. NYSIIS was chosen as the selected metric. To expedite the process an initial search was performed for controlled keys that had the highest number of near-collision keys, this was due to the demonstration of the actual generation of keys. Producing near-matching keys that have a very small number of potential matches, therefore, adds very little to this demonstration with a large computation cost.
